Smart Model Elimination for Efficient Automated Machine Learning

### 2024-06-22 paper/paper.tex
urls

[1] He, Xin, et al. “AutoML: A Survey of the State-of-the-Art.” Knowledge-Based Systems, journal-article, 16 Apr. 2021, arxiv.org/pdf/1908.00709.

@@

[3] Global Strategy on Human Resources for Health: Workforce 2030. World Health Organization, 2016, iris.who.int/bitstream/handle/10665/250368/9789241511131-eng.pdf?sequence=1.

@@

[6] “H2oai/H2o-3: H2O Is an Open Source, Distributed, Fast and Scalable Machine Learning Platform: Deep Learning, Gradient Boosting (GBM) \& XGBoost, Random Forest, Generalized Linear Modeling (GLM With Elastic Net), K-Means, PCA, Generalized Additive Models (GAM), RuleFit, Support Vector Machine (SVM), Stacked Ensembles, Automatic Machine Learning (AutoML), Etc.” GitHub, github.com/h2oai/h2o-3.

[7] Olson, Randal S., 1, et al. Automating Biomedical Data Science Through Tree-based Pipeline Optimization. journal-article, 28 Jan. 2016, arxiv.org/pdf/1601.07925.

[8] “EpistasisLab/Tpot: A Python Automated Machine Learning Tool That Optimizes Machine Learning Pipelines Using Genetic Programming.” GitHub, github.com/EpistasisLab/tpot.

[9] “Mljar/Mljar-supervised: Python Package for AutoML on Tabular Data With Feature Engineering, Hyper-Parameters Tuning, Explanations and Automatic Documentation.” GitHub, github.com/mljar/mljar-supervised.

@@

[11] Shang, Zhi, et al. "FLAML: A Fast and Lightweight AutoML Library." arXiv, 11 Nov. 2019, arxiv.org/pdf/1911.04706.

[12] "FLAML: A Fast Library for AutoML and Tuning." GitHub, github.com/microsoft/FLAML.

[13] “Sb-ai-lab/LightAutoML: Fast and Customizable Framework for Automatic ML Model Creation (AutoML).” GitHub, github.com/sb-ai-lab/LightAutoML.

[14] Akalin, Altuna. 3.3 Relationship Between Variables: Linear Models and Correlation | Computational Genomics With R. 30 Sept. 2020, compgenomr.github.io/book/relationship-between-variables-linear-models-and-correlation.html.

[15] Lung Cancer. 15 July 2022, www.kaggle.com/datasets/nancyalaswad90/lung-cancer.

[16] Chronic KIdney Disease Dataset. 13 Apr. 2017, www.kaggle.com/datasets/mansoordaku/ckdisease.

[17] Busekseolu. Diabetes Classification. 26 Nov. 2021, www.kaggle.com/code/busekseolu/diabetes-classification/input.

[18] Mahendrasinghrajpoot. Brain Stroke Dataset. 21 Aug. 2022, www.kaggle.com/code/mahendrasinghrajpoot/brain-stroke-dataset/input.

[19] Thomaskonstantin. Analyzing and Modeling Stroke Data. 6 July 2021, www.kaggle.com/code/thomaskonstantin/analyzing-and-modeling-stroke-data/input.

[20] Robikscube. Eye State Prediction Dataset. 26 June 2022, www.kaggle.com/code/robikscube/eye-state-prediction-dataset/input?select=EEG_Eye_State_Classification.csv.

>>>>

[1] He, Xin, et al. “AutoML: A Survey of the State-of-the-Art.” Knowledge-Based Systems, journal-article, 16 Apr. 2021, \url{arxiv.org/pdf/1908.00709}.

@@

[3] Global Strategy on Human Resources for Health: Workforce 2030. World Health Organization, 2016, \url{iris.who.int/bitstream/handle/10665/250368/9789241511131-eng.pdf?sequence=1}.

@@

[6] “H2oai/H2o-3: H2O Is an Open Source, Distributed, Fast and Scalable Machine Learning Platform: Deep Learning, Gradient Boosting (GBM) \& XGBoost, Random Forest, Generalized Linear Modeling (GLM With Elastic Net), K-Means, PCA, Generalized Additive Models (GAM), RuleFit, Support Vector Machine (SVM), Stacked Ensembles, Automatic Machine Learning (AutoML), Etc.” GitHub, \url{github.com/h2oai/h2o-3}.

[7] Olson, Randal S., 1, et al. Automating Biomedical Data Science Through Tree-based Pipeline Optimization. journal-article, 28 Jan. 2016, \url{arxiv.org/pdf/1601.07925}.

[8] “EpistasisLab/Tpot: A Python Automated Machine Learning Tool That Optimizes Machine Learning Pipelines Using Genetic Programming.” GitHub, \url{github.com/EpistasisLab/tpot}.

[9] “Mljar/Mljar-supervised: Python Package for AutoML on Tabular Data With Feature Engineering, Hyper-Parameters Tuning, Explanations and Automatic Documentation.” GitHub, \url{github.com/mljar/mljar-supervised}.

@@

[11] Shang, Zhi, et al. "FLAML: A Fast and Lightweight AutoML Library." arXiv, 11 Nov. 2019, \url{arxiv.org/pdf/1911.04706}.

[12] "FLAML: A Fast Library for AutoML and Tuning." GitHub, \url{github.com/microsoft/FLAML}.

[13] “Sb-ai-lab/LightAutoML: Fast and Customizable Framework for Automatic ML Model Creation (AutoML).” GitHub, \url{github.com/sb-ai-lab/LightAutoML}.

[14] Akalin, Altuna. 3.3 Relationship Between Variables: Linear Models and Correlation | Computational Genomics With R. 30 Sept. 2020, \url{compgenomr.github.io/book/relationship-between-variables-linear-models-and-correlation.html}.

[15] Lung Cancer. 15 July 2022, \url{www.kaggle.com/datasets/nancyalaswad90/lung-cancer}.

[16] Chronic KIdney Disease Dataset. 13 Apr. 2017, \url{www.kaggle.com/datasets/mansoordaku/ckdisease}.

[17] Busekseolu. Diabetes Classification. 26 Nov. 2021, \url{www.kaggle.com/code/busekseolu/diabetes-classification/input}.

[18] Mahendrasinghrajpoot. Brain Stroke Dataset. 21 Aug. 2022, \url{www.kaggle.com/code/mahendrasinghrajpoot/brain-stroke-dataset/input}.

[19] Thomaskonstantin. Analyzing and Modeling Stroke Data. 6 July 2021, \url{www.kaggle.com/code/thomaskonstantin/analyzing-and-modeling-stroke-data/input}.

[20] Robikscube. Eye State Prediction Dataset. 26 June 2022, \url{www.kaggle.com/code/robikscube/eye-state-prediction-dataset/input?select=EEG_Eye_State_Classification.csv}.
